analysis_stable

### 2020-08-14 inst/analysis/analysis_stable.Rmd
Call sites with parse, classification per type

@@

In terms of call sites, there are `r nb_parsed_call_sites` i.e. `r nb_parsed_call_sites / nb_call_sites * 100`.

@@

```{r}
nb_file <- parsed_evals_args %>% filter(!is.na(parse_args_file)) %>% nrow()
```

```{r}
nb_text <- parsed_evals_args %>% filter(!is.na(parse_args_text)) %>% nrow()
```

@@

>>>>

### Classifying according to the type of the `expr` argument

```{r types}
per_expr_type <- eval_calls %>% count(expr_expression_type)
```

```{r}
 per_expr_type %>% mutate(per_cent = n / nb_eval_calls * 100 ) %>% arrange(desc(n)) %>% knitr::kable()
```

```{r}
per_expr_type %>% ggplot() +
  geom_col(aes(x = fct_reorder(expr_expression_type, n), y = n)) +
  scale_y_sqrt() + 
  coord_flip() +
  labs(title = "Calls per type", y = "n", x = "type" ) 
```

<details> 
  <summary>Expressions left unchanged by <code>eval</code></summary>

Expressions of types other than `call`,  `expression`, `name`, `bytecode` and `promise` are just returned unchanged. Here `language` refers to `call` , `name`to `symbol`. `bytecode` refers to bytecode objects, that are generated by the `compile`function:

```{r}
typeof(compiler::compile(1+1))
```

```{r not_unchanged_eval}
changed_evals <- eval_calls %>% mutate(changed =  fct_collapse(expr_expression_type, base_types = c("LANGSXP", "EXPRSXP", "SYMSXP", "PROMSXP", "BCODESXP"))) %>% count(changed) %>% mutate(per_cent = n / nb_eval_calls * 100 ) 
```

We can remove `eval` and leave there the expression in `r changed_evals[2, "per_cent"][[1]]`% of the eval calls (i.e. `r changed_evals[2, "n"][[1]]`).

@@

In terms of call sites, there are `r nb_parsed_call_sites` i.e. `r nb_parsed_call_sites / nb_call_sites * 100`%.

@@

```{r}
parsed_files <- parsed_evals_args %>% filter(!is.na(parse_args_file))
nb_file <- parsed_files %>% nrow()
nb_file_call_sites <- nb_eval_call_sites(parsed_files)
```

```{r}
parsed_texts <- parsed_evals_args %>% filter(!is.na(parse_args_text) | !is.na(parse_args_s))
nb_text <-  parsed_texts %>% nrow()
nb_text_call_sites <- nb_eval_call_sites(parsed_texts)
```

@@

There are `r nb_file_call_sites` call sites with the `file` argument, and `r nb_text_call_sites` with the `text` argument, i.e. `r  nb_file_call_sites / nb_parsed_call_sites * 100`%, and `r nb_text_call_sites / nb_parsed_call_sites *100`% respectively.
